The title

### 2018-04-26 writeup.Rmd
more intro

1. 
  a. *Utterance:* Some of her pets are cats.
  b. *Implicature:* Some, but not all, of her pets are cats.
  c. *Scale:* <all, some>

2. 
  a. *Utterance:* She owns a cat or a dog.
  b. *Implicature:* She owns a cat or a dog, but not both.
  c. *Scale:* <and, or>

>>>>

1. 
  + *Utterance:* Some of her pets are cats.
  + *Implicature:* Some, but not all, of her pets are cats.
  + *Scale:* <all, some>

2. 
  + *Utterance:* She owns a cat or a dog.
  + *Implicature:* She owns a cat or a dog, but not both.
  + *Scale:* <and, or>
